Challenges to the Two-Infall Scenario by Large Stellar Age Catalogs

### 2025-05-16 src/tex/ms.tex

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{src/tex/figures/ofe_distribution_params.pdf}
    \caption{Stellar [O/Fe] distributions produced by select multi-zone models with \yZ{2} (a--d) and as observed by APOGEE (e). The layout is similar to Figure \ref{fig:abundance-evolution-yields}. Each column shows results from a different multi-zone model: {\bf (a)} the fiducial model with \yZ{2}, the fiducial DTD, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$ (identical to column (b) of Figure \ref{fig:abundance-evolution-yields}); {\bf (b)} a model that adopts a power-law DTD; {\bf (c)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$; and {\bf (d)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.5$. {\bf Key takeaway:} For the \yZ{2} case, pre-enrichment of the accreted gas or a higher thick-to-thin disk ratio can improve the low-$\alpha$ distribution while preserving the high-$\alpha$ peak.}
    \label{fig:ofe-distribution-parameters}
\end{figure*}

@@

Next, in model (c) the metallicity of the infalling gas increases to $\mathXH_{\rm CGM}=-0.5$ at late times. We choose this value because it is the maximum which can plausibly still reproduce the disk abundances; any higher and the infalling gas would be more metal-rich than the most metal-poor thin disk stars. This model results in very similar [O/Fe] distributions to the $y/Z_\odot=1$ case. We assume that the infalling gas has $\mathOFe=0$ at all times; an alternate run with $\mathOFe=+0.3$ shifted the distribution towards higher [O/Fe], worsening agreement with observations. 
% In summary, pre-enriched gas infall may be necessary for the two-infall model to match the observed [O/Fe] distribution across the disk.

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/ofe_feh_best.pdf}
    \caption{Stellar abundance distributions across the disk predicted by our best multi-zone model, with \yZ{2}, ${\rm [X/H]}_{\rm CGM}=-0.7$, $f_\Sigma(R_\odot)=0.25$, $\sigma_{\rm RM8}=3.6\kpc$, and $\eta_\odot=1.8$. Each panel presents a random mass-weighted sample of \num{10000} stellar populations that are drawn from the given ($R_{\rm gal}$, $|z|$) bin and color-coded by age. A Gaussian scatter is applied to each point according to the median age ($\tau_{\rm NN}$) and abundance uncertainties in Table \ref{tab:uncertainties}. The solid and dashed contours enclose 30\% and 80\%, respectively, of the APOGEE data in each region. {\bf Key takeaway:} The predicted distribution from the two-infall model lines up with the APOGEE distribution close to the midplane, but agreement is worse at higher latitudes and in the outer Galaxy.}
    \label{fig:ofe-feh-best}
\end{figure*}

>>>>

\todo{Discuss why we divided Figures \ref{fig:ofe-distribution-yields} and \ref{fig:ofe-distribution-parameters} into $|z|$ bins: (1) pattern changes as a function of midplane distance, and (2) we don't have to worry so much about correcting the APOGEE data to rebalance between the thin and thick disk fields.}

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{src/tex/figures/ofe_distribution_params.pdf}
    \caption{Stellar [O/Fe] distributions produced by select multi-zone models with \yZ{2} (a--d) and as observed by APOGEE (e). The layout is similar to Figure \ref{fig:ofe-distribution-yields}. Each column shows results from a different multi-zone model: {\bf (a)} the fiducial model with \yZ{2}, the fiducial DTD, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$ (identical to column (b) of Figure \ref{fig:abundance-evolution-yields}); {\bf (b)} a model that adopts a power-law DTD; {\bf (c)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$; and {\bf (d)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.5$. {\bf Key takeaway:} For the \yZ{2} case, pre-enrichment of the accreted gas or a higher thick-to-thin disk ratio can improve the low-$\alpha$ distribution while preserving the high-$\alpha$ peak.}
    \label{fig:ofe-distribution-parameters}
\end{figure*}

@@

Next, in model (c) the metallicity of the infalling gas increases to $\mathXH_{\rm CGM}=-0.5$ at late times. We choose this value because if it were any higher, the infalling gas would have higher metallicity than the most metal-poor thin disk stars. This model results in very similar [O/Fe] distributions to the $y/Z_\odot=1$ case. We assume that the infalling gas has $\mathOFe=0$ at all times; an alternate run with $\mathOFe=+0.3$ shifted the distribution towards higher [O/Fe], worsening agreement with observations. 
% In summary, pre-enriched gas infall may be necessary for the two-infall model to match the observed [O/Fe] distribution across the disk.

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/ofe_feh_best.pdf}
    \caption{Stellar abundance distributions across the disk predicted by our best multi-zone model, with \yZ{2}, ${\rm [X/H]}_{\rm CGM}=-0.7$, $f_\Sigma(R_\odot)=0.25$, $\sigma_{\rm RM8}=3.6\kpc$, and $\eta_\odot=1.8$. Each panel presents a random mass-weighted sample of \num{10000} stellar populations that are drawn from the given ($R_{\rm gal}$, $|z|$) bin and color-coded by age. A Gaussian scatter is applied to each point according to the median age ($\tau_{\rm [C/N]}$) and abundance uncertainties in Table \ref{tab:uncertainties}. The solid and dashed contours enclose 30\% and 80\%, respectively, of the APOGEE data in each region. {\bf Key takeaway:} The predicted distribution from the two-infall model lines up with the APOGEE distribution close to the midplane, but agreement is worse at higher latitudes and in the outer Galaxy.}
    \label{fig:ofe-feh-best}
\end{figure*}
